Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
more text on human judgments in paradigm section

\subsection{Reference evaluation measures}

TO DO: TALK ABOUT HUMAN F/A JUDGMENTS

When considering a candidate measure $m$, reporting correlations of
$m$ with absolute HTER scores can conflate $m$'s power in identifying
which of two candidate translations is better with $m$'s (and HTER)'s
ability to distinguish which of two source documents is more difficult
to translate. To avoid this conflation, we consider the mean-removed
$m$ and HTER scores; this lowers the correlations but ensures that the
reported correlations are among differences in the translations rather
than among differences in the underlying document.

>>>>

\subsection{Reference evaluation measures over parallel translations}

For some of the experiments presented here (sections~\ref{sec:hter1}
and~\ref{sec:hter2}), we have multiple translations of the same source
segment, each from a different translation engine and each with its
own HTER score.  For these translations, reporting correlations of
metric $m$ with absolute HTER scores can conflate $m$'s power in
identifying which of two candidate translations is better with $m$'s
(and HTER)'s ability to distinguish which source segments are
more difficult to translate.

To avoid this conflation, on the HTER corpora we report correlations of
the mean-removed $m$ and HTER scores. Mean-removal  lowers the
correlation $r$ values reported but
ensures that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.

Section~\ref{sec:hter2} reports HTER correlations per-sentence. There,
we use length-weighted correlation, since unweighted correlations
effectively puts too much emphasis on short sentences.  We do not
weight for length in section~\ref{sec:hter1}, which reports document
correlations, because documents are assumed to be equally important
(regardless of length).
